Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-08-07 tex/ms.tex
small wording changes in discussion

We have demonstrated, using a sample of stellar clusters in M31, that
we can combine photometric and spectroscopic data in a principled way
to infer physical properties.  We do not resort to an arbitrary
down-weighting or up-weighting of certain data. Instead, we explicitly
model our uncertain knowledge of the spectral calibration and infer
this calibration jointly with the physical properties. For a number of
applications this combination of spectroscopy and photometry reduces
the need for spectrophotometric calibration, such that the less
expensive photometry is sufficient.  Additional calibration
information, if it exists, can be incorporated into informative priors
on the calibration parameters of the model, or inform the construction
of the calibration model.

>>>>

We have demonstrated, using a sample of stellar clusters in M31, that
we can combine photometric and spectroscopic data in a principled way
to infer physical properties.  We do not resort to an arbitrary
down-weighting or up-weighting of certain data. Instead, we explicitly
model our uncertain knowledge of the spectral calibration and infer
this calibration jointly with the physical properties. For a number of
applications this combination of spectroscopy and photometry reduces
the need for spectrophotometric calibration entirely, such that the less
expensive photometry is sufficient.  Additional calibration
information, if it exists, can be incorporated into informative priors
on the calibration parameters of the model, to inform the construction
of the calibration model, or to approximately remove gross features
that are difficult to model parameterically or as a sum of Gaussians.
